---
title: "Braun et al, 2021 analysis"
author: "Alfons Edmar"
date: "2023-02-15"
output: html_document
---
# Packages
```{r}
library(tidyverse)
library(readxl)
library(here)
library(snakecase)
```
# Variable coding 

This is the authors explaining the coding: 
Explanatory Role: 
1 = explanatory
2 = non-explanatory

Correction Condition 
1 = no correct 
2 = negation
3 = negation + alternative 

Misinformation
0 = control 
1 = misled


# Experiment 1
No analysis of experiment 1 is possible since no indicator for control items are present. 

# Experiment 2 
```{r}
data <- read_excel(
    path = here("open_data_analyses/data/Braun_et_al_2021 .xlsx"), 
    sheet = "Experiment 2")

clean_data <- filter(data, data$`Participated in E1` != 1)

names(clean_data) <- to_any_case(
  string = names(data), case = 'snake')
clean_data <- rename(clean_data,
                     c('tp_recall' = tp_free_recall
                       ,'spider_recall' = spider_free_recall
                       , 'tp_correct' = tp_corect
                       , 'ex_role' = explanatory_role))
#note. we have 2 more participants than reported in the paper. 
```
We want to look at the free recall proportions for the misinformed and non-misinformed individuals. I interpret a 0 in the free recall to mean that the did not recall. 
```{r}
misled <- clean_data %>%
  filter(misinformation == 1) %>%
  select(spider_recall, tp_recall, ex_role, 
         tp_correct, spider_correct)

control <- clean_data %>%
  filter(misinformation == 0) %>%
  select(spider_recall, tp_recall, ex_role, 
         tp_correct, spider_correct )
```


# Mean proportions by treatment conditions as seen in fig.5

Here is the mean and sd for the tp prank question for the misled 
```{r}
#explanatory no correction
mean(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 1])

#explanatory negation
mean(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 2])

#no explanatory and no correction
mean(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 1])

#no explanatory with negation
mean(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 2])
```
Here is the mean and sd for the spider question for the misled
```{r}
#explanatory no correction
mean(misled$spider_recall[misled$spider_correct == 1
                          & misled$ex_role == 1])

#explanatory negation
mean(misled$spider_recall[misled$spider_correct == 1 
                          & misled$ex_role == 2])

#no explanatory and no correction
mean(misled$spider_recall[misled$spider_correct == 2 
                          & misled$ex_role == 1])

#no explanatory with negation
mean(misled$spider_recall[misled$spider_correct == 2 
                          & misled$ex_role == 2])
```
Here is the mean and sd for the tp prank on the control group. Note that no individual in the control group were misled, therefore the explanatory role variable means nothing. They were however corrected.
```{r}
#tp no correction
mean(control$tp_recall[control$tp_correct == 1])

#tp correction
mean(control$tp_recall[control$tp_correct == 2])

#note. there is only one recall of TP 

```
Here is the mean and sd for the spider question on the control group
```{r}
#no spider correct
mean(control$spider_recall[control$spider_correct == 1])

# spider correction
mean(control$spider_recall[control$spider_correct == 2])
```

Extracting number of participants in the different groups. 

TP:
```{r}
#explanatory no correction
NROW(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 1])

#explanatory negation
NROW(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 2])

#no explanatory and no correction
NROW(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 1])

#no explanatory with negation
NROW(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 2])
```
Spider: 
```{r}
#explanatory no correction
NROW(misled$spider_recall[misled$spider_correct == 1
                          & misled$ex_role == 1])

#explanatory negation
NROW(misled$spider_recall[misled$spider_correct == 1 
                          & misled$ex_role == 2])

#no explanatory and no correction
NROW(misled$spider_recall[misled$spider_correct == 2 
                          & misled$ex_role == 1])

#no explanatory with negation
NROW(misled$spider_recall[misled$spider_correct == 2 
                          & misled$ex_role == 2])
```
Control:
```{r}
# tp no correction
NROW(control$tp_recall[control$tp_correct == 1])

#tp correction
NROW(control$tp_recall[control$tp_correct == 2])

#spider no correction
NROW(control$spider_recall[control$spider_correct == 1])

# spider correction
NROW(control$spider_recall[control$spider_correct == 2])
```







