---
title: "Braun et al, 2021 analysis"
author: "Alfons Edmar"
date: "2023-02-15"
output: html_document
---
# Packages
```{r}
library(tidyverse)
library(readxl)
library(here)
```
# Variable coding 

This is the authors explaining the coding: 
Explanatory Role: 
1 = explanatory
2 = non-explanatory

Correction Condition 
1 = no correct 
2 = negation
3 = negation + alternative 

Misinformation
0 = control 
1 = misled


# Experiment 2 
```{r}
data <- read_excel(
    path = here("open_data_analyses/data/Braun_et_al_2021 .xlsx"), 
    sheet = "Experiment 2")
clean_data <- filter(data, data$`Participated in E1` != 1)
clean_data <- rename(clean_data,
                     c('tp_recall' = `TP Free Recall`
                       ,'spider_recall' = `Spider Free Recall`
                       ,'tp_correct' = `TP Corect`
                       , 'spider_correct' = `Spider Correct`
                       , 'ex_role' = `Explanatory Role`))
#note. we have 2 more participants than reported in the paper. 
```
We want to look at the free recall proportions for the misinformed and non-misinformed individuals. I interpret a 0 in the free recall to mean that the did not recall. 
```{r}
misled <- clean_data %>%
  filter(Misinformation == 1) %>%
  select(spider_recall, tp_recall, ex_role, 
         tp_correct, spider_correct)

control <- clean_data %>%
  filter(Misinformation == 0) %>%
  select(spider_recall, tp_recall, ex_role, 
         tp_correct, spider_correct )
```


# Mean proportions by treatment conditions as seen in fig.5

Here is the mean and sd for the tp prank question for the misled 
```{r}
#explanatory no correction
mean(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 1])
sd(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 1])

#explanatory negation
mean(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 2])
sd(misled$tp_recall[misled$tp_correct == 1 & misled$ex_role == 2])

#no explanatory and no correction
mean(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 1])
sd(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 1])

#no explanatory with negation
mean(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 2])
sd(misled$tp_recall[misled$tp_correct == 2 & misled$ex_role == 2])
```
Here is the mean and sd for the spider question for the misled
```{r}
#explanatory no correction
mean(misled$spider_recall[misled$spider_correct == 1
                          & misled$ex_role == 1])
sd(misled$spider_recall[misled$spider_correct == 1 
                        & misled$ex_role == 1])

#explanatory negation
mean(misled$spider_recall[misled$spider_correct == 1 
                          & misled$ex_role == 2])
sd(misled$spider_recall[misled$spider_correct == 1 
                        & misled$ex_role == 2])

#no explanatory and no correction
mean(misled$spider_recall[misled$spider_correct == 2 
                          & misled$ex_role == 1])
sd(misled$spider_recall[misled$spider_correct == 2 
                        & misled$ex_role == 1])

#no explanatory with negation
mean(misled$spider_recall[misled$spider_correct == 2 
                          & misled$ex_role == 2])
sd(misled$spider_recall[misled$spider_correct == 2 
                        & misled$ex_role == 2])
```
Here is the mean and sd for the tp prank on the control group
```{r}
#explanatory 
mean(control$tp_recall[control$ex_role == 1])
sd(control$tp_recall[control$ex_role == 1])

#non-explanatory
mean(control$tp_recall[control$ex_role == 2])
sd(control$tp_recall[control$ex_role == 2])

#note. there is only one recall of TP 

```
Here is the mean and sd for the spider question on the control group
```{r}
#explanatory 
mean(control$spider_recall[control$ex_role == 1])
sd(control$spider_recall[control$ex_role == 1])

#non-explanatory
mean(control$spider_recall[control$ex_role == 2])
sd(control$spider_recall[control$ex_role == 2])

#note. there is only one recall of TP 
```




