---
title: "Analysis of Chan et al, (2022)"
author: "Alfons Edmar"
date: "2023-03-23"
output: html_document
---

Packages:
```{r}
library(readr)
library(here)
library(tidyverse)
library(snakecase)
```


# Study 1

Data:
```{r}
study_1 <- read_csv(here(
  "open_data_analyses/data/Chan_et_al_2022_study_1.csv"))
```

Variables:

cond: Test condition (i.e., Tested or Nontested)
warn: Warning condition (i.e., Warned or Unwarned)
mi_c: final test accuracy for misled items, correct responses
cong_c: final test accuracy for consistent items, correct responses

Wrangling:
```{r}
# Changling variable names
names(study_1) <- to_snake_case(names(study_1))
# Extracting variables of interest
study_1 <- study_1 %>% select(cond, warn, mi_c, cong_c)
```


Accuracy on misled and non-misled items across conditions:
```{r}
# mean for misled items
round(tapply(
  study_1$mi_c,list(study_1$cond, study_1$warn),mean), 3)

# sd for misled items
round(tapply(
  study_1$mi_c,list(study_1$cond, study_1$warn),sd), 3)

# consistent items
round(tapply(
  study_1$cong_c,list(study_1$cond, study_1$warn),mean), 3)

# sd for consistent items
round(tapply
      (study_1$cong_c,list(study_1$cond, study_1$warn),sd), 3)
```

Sample size across conditions:
```{r}
tapply(study_1$mi_c,list(study_1$cond, study_1$warn),NROW)
```
# Study 2

Data:
```{r}
study_2 <- read_csv(here(
  "open_data_analyses/data/Chan_et_al_2022_study_2.csv"))
```



# Study 1

Data:
```{r}
study_1 <- read_csv(here(
  "open_data_analyses/data/Chan_et_al_2022_study_1.csv"))
```


Wrangling:
```{r}
# Changling variable names
names(study_2) <- to_snake_case(names(study_2))
# Extracting variables of interest
study_2 <- study_2 %>% select(cond, warn, mi_c, cong_c)
```


Accuracy on misled and non-misled items across conditions:
```{r}
# mean for misled items
round(tapply(
  study_2$mi_c,list(study_2$cond, study_2$warn),mean), 3)

# sd for misled items
round(tapply(
  study_2$mi_c,list(study_2$cond, study_2$warn),sd), 3)

# consistent items
round(tapply(
  study_2$cong_c,list(study_2$cond, study_2$warn),mean), 3)

# sd for consistent items
round(tapply(
  study_2$cong_c,list(study_2$cond, study_2$warn),sd), 3)
```

Sample size across conditions:
```{r}
tapply(study_2$mi_c,list(study_2$cond, study_2$warn),NROW)
```

# Study 3

```{r}
study_3 <- read_csv(here(
  "open_data_analyses/data/Chan_et_al_2022_study_3.csv"))
```


Wrangling:
```{r}
# Changling variable names
names(study_3) <- to_snake_case(names(study_3))
# Extracting variables of interest
study_3 <- study_3 %>% select(cond, warn, mi_c, cong_c)
```


Accuracy on misled and non-misled items across conditions:
```{r}
# mean for misled items
round(tapply(
  study_3$mi_c,list(study_3$cond, study_3$warn),mean), 3)

# sd for misled items
round(tapply(
  study_3$mi_c,list(study_3$cond, study_3$warn),sd), 3)

# consistent items
round(tapply(
  study_3$cong_c,list(study_3$cond, study_3$warn),mean), 3)

# sd for consistent items
round(tapply(
  study_3$cong_c,list(study_3$cond, study_3$warn),sd), 3)
```

Sample size across conditions:
```{r}
tapply(study_3$mi_c,list(study_3$cond, study_3$warn),NROW)
```

